Proposed Solution

### 2017-04-15 PLDI/secs/abs.tex
fix words

\begin{abstract}

System failures resulting from configuration errors are one of the major reasons for compromised reliability of today's software systems. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred. 
Verifying configuration files is, nevertheless, a challenging problem, because 
  1) software configurations are typically written in poorly structured and untyped ``languages'', and 
  2) specifying rules for configuration verification is challenging in practice.
This paper presents \app, a verification framework for general software configurations.
Our framework works as follows: in the pre-processing stage, we first automatically derive a specification.
Once we have a specification, we check if a given configuration file adheres to that specification.
The process of learning specification works through three steps.
First, \app parses a training set of configuration files (not necessarily all correct) into a well-structured and probabilistically-typed intermediate representation.
Second, based on the association rule learning algorithm \app learns rules from these intermediate representations. 
These rules establish relationships between the keywords appearing in the files. 
Finally, \app employs rule graph analysis to refine the resulting rules. 
\app is capable of detecting various configuration errors, including ordering errors, integer correlation errors, type errors, and missing entry errors. 
We evaluated \app by verifying public configuration files on Github, and we show that \app can detect known configuration errors in these files.

\end{abstract}

>>>>

System failures resulting from configuration errors are one of the major reasons for the compromised reliability of today's software systems. 
Although many techniques have been proposed for configuration error detection, these approaches can generally only be applied after an error has occurred. 
Proactively verifying configuration files is a challenging problem, because 
  1) software configurations are typically written in poorly structured and untyped ``languages'', and 
  2) specifying rules for configuration verification is challenging in practice.
This paper presents \app, a verification framework for general software configurations.
Our framework works as follows: in the pre-processing stage, we first automatically derive a specification.
Once we have a specification, we check if a given configuration file adheres to that specification.
The process of learning a specification works through three steps.
First, \app parses a training set of configuration files (not necessarily all correct) into a well-structured and probabilistically-typed intermediate representation.
Second, based on the association rule learning algorithm, \app learns rules from these intermediate representations. 
These rules establish relationships between the keywords appearing in the files. 
Finally, \app employs rule graph analysis to refine the resulting rules. 
\app is capable of detecting various configuration errors, including ordering errors, integer correlation errors, type errors, and missing entry errors. 
We evaluated \app by verifying public configuration files on Github, and we show that \app can detect known configuration errors in these files.

### 2017-04-15 PLDI/secs/arch.tex
fix words

\para{Learning}
The learner converts the intermediate representation from the translator to a set of rules.
It employs variation on the {\em rule association 
algorithm}~\cite{agrawal1993mining}, to generate this list of rules, which describe properties of a correct configuration file. 
This is a probabilistic verification approach that learns a specification for a correct file over an unlabeled training set of both correct and incorrect configurations files.
The learning algorithm uses various instances of a rule interface to learn different classes of rules, such as ordering or integer relations.
These rules are then considered to be required for any configuration files to be correct, and can be used for verification.

\para{Post Analysis}
Finally, the logically structured representation of learned rules allows for a further \textit{rule graph analysis}.
We introduce the concept of a rule graph that can be built from the output of the modified association rule learning algorithm.
We analyze the properties of this graph to construct an ordering of rules by their importance, 
  as well as to produce a measure of complexity for any configuration of the target system.
While the metrics in used in \app are effective, they are not intended to be exhaustive.
The information contained in the structured representation of the learned rules, 
  is a unique benefit of the learning algorithm, that has potential to be leveraged in many new ways.

>>>>

\para{Learning}
The learner converts the intermediate representation from the translator to a set of rules.
It employs variation on the {\em association rule 
algorithm}~\cite{agrawal1993mining}, to generate this list of rules, which describe properties of a correct configuration file. 
This is a probabilistic verification approach that learns a specification for a correct file over an unlabeled training set of both correct and incorrect configurations files.
The learning algorithm uses various instances of a rule interface to learn different classes of rules, such as ordering or integer relations.
These rules are then considered to be required for any configuration files to be correct, and can be used for verification.

\para{Rule Graph Analysis}
Finally, the logically structured representation of learned rules allows for a further \textit{rule graph analysis}.
The purpose of this module is to refine the learned rules.
To this end, we introduce the concept of a rule graph that can be built from the output of the modified association rule learning algorithm.
We analyze the properties of this graph to construct a ranking of rules by their importance, 
  as well as to produce a measure of complexity for any configuration of the target system.
While the metrics in used in \app are effective, they are not intended to be exhaustive.
The information contained in the structured representation of the learned rules, 
  is a unique benefit of the learning algorithm, that has potential to be leveraged in many new ways.

### 2017-04-15 PLDI/secs/intro.tex
fix words

\item We propose the first automatic configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.

>>>>

\item We propose a configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.

### 2017-04-15 PLDI/secs/motiv.tex
fix words

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  max_connections               = 64
  thread_cache_size             = 8
  thread_concurrency            = 8

  key_buffer_size               = 4G
  max_heap_table_size           = 128M

  join_buffer_size              = 32M
  sort_buffer_size              = 32M    
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
FINE GRAINED ERROR: Expected 
  "max_connections" * "sort_buffer_size" >= "key_buffer_size"
\end{lstlisting}

>>>>

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  max_connections               = 64
  thread_cache_size             = 8
  thread_concurrency            = 8
  key_buffer_size               = 4G
  max_heap_table_size           = 128M
  join_buffer_size              = 32M
  sort_buffer_size              = 32M    
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
FINE GRAINED ERROR: Expected 
  "max_connections" * "sort_buffer_size" > "key_buffer_size"
\end{lstlisting}

### 2017-04-15 PLDI/secs/postanal.tex
fix words

\section{rule graph Analysis}
\label{sec-post}

@@

Keywords (specifically their corresponding vertices)
of low $\mathcal{D}(v)$ may be rarer configuration
parameters where rules learned are more likely to be governed by 
tehchnical necessity, rather than industry convention. As such, errors
reported involving low-degree keywords are more likely to be errors
of high significance and should be presented with high importance
to users of \app.

>>>>

\section{Rule Graph Analysis}
\label{sec-post}

@@

Keywords (specifically their corresponding vertices)
of low $\mathcal{D}(v)$ may be rarer configuration
parameters where rules learned are more likely to be governed by 
technical necessity, rather than industry convention. As such, errors
reported involving low-degree keywords are more likely to be errors
of high significance and should be presented with high importance
to users of \app.

### 2017-04-15 PLDI/secs/trans.tex
fix words

In order to define resolution predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |int\ptype| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
We then can run inference on that sample training set to derive a probabilistic type \texttt{bar}$:[bool=3,int=1]$.
This is then resolved, as required in our earlier example, to \texttt{bar}$::bool$.

Note that a user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
For example, if a user instead picked $p_{int}(\ptype)= |int\ptype| \geq 1$, {\scriptsize INT} would overlap with {\scriptsize BOOL}.
To resolve the ambiguity in this case, we must add a new rule {\scriptsize INTBOOL} that introduces a new, internal type $intbool$ to be created when both resolution predicates are true.
The antecedent statement of {\scriptsize INT} must also be updated to $p_{int}(\ptype) \land \neg p_{bool}(\ptype)$, and likewise with {\scriptsize BOOL}.
The $intbool$ type is only a placeholder to be used with the additional subtyping relations $intbool <: int$ and $intbool <: bool$
These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keywords may be compared in the {\scriptsize EQ\_RULE}.

>>>>

In order to define resolution predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool_{\ptype}| \geq 3 \land |int_{\ptype}| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
We then can run inference on that sample training set to derive a probabilistic type \texttt{bar}$:[bool=3,int=1]$.
This is then resolved, as required in our earlier example, to \texttt{bar}$::bool$.

Note that a user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
For example, if a user instead picked $p_{int}(\ptype)= |int\ptype| \geq 1$, {\scriptsize INT} would overlap with {\scriptsize BOOL}.
This means that types are not unique in this system, i.e. $k:\ptype \land k:\ptype' \centernot\implies \ptype = \ptype'$.

To resolve the ambiguity in this case, we must add a new rule {\scriptsize INTBOOL} that introduces a new, internal type $intbool$ to be created when both resolution predicates are true.
The antecedent statement of {\scriptsize INT} must also be updated to $p_{int}(\ptype) \land \neg p_{bool}(\ptype)$, and likewise with {\scriptsize BOOL}.
The $intbool$ type is only a placeholder to be used with the additional subtyping relations $intbool <: int$ and $intbool <: bool$
These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keywords may be compared in the {\scriptsize EQ\_RULE}.
